---
title: "Set up new study area"
subtitle: "Example workflow #2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Set up new study area}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
## NOTE to regenerate all of the results of this Rmd
## some chunks will need to be run manually prior to
## knitting the report
## i.e. ones that generate graphics.

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, warning=FALSE}
#devtools::load_all("D:\\PEM_DATA\\PEMsamplr")
#devtools::load_all("D:\\PEM_DATA\\PEMprepr")

library(PEMprepr)
library(ggplot2)
library(sf)
library(terra)

```

`PEMprepr`, short for _Predictive Ecosystem Mapping -- Preparation_ is the first of a
series of packages supporting the British Columbia Biogeoecosystem Classification's
Predictive Ecosystem Mapping (PEM) project.  See [BC-BEC](https://www.for.gov.bc.ca/HRE/becweb/index.html)
and [`PEMr`](https://github.com/bcgov/PEMr) on _GitHub_for details about the BC BEC classification system and, the PEM Project.

In the example below it is assumed that you are running the following within a new R project.


## Project Set up. 

1) Set up a new R studio project for your PEM modelling. 
2) For each study area we will generate a folder and associated folder structure.
3) Example we will create an example project called "CanyonCreek"


```{r}
# set up the folder structure and define folder names in object fid
fid <- setup_folders("CanyonCreek")

```


# Folder setup

Data for the project can quickly become difficult to manage.  To facilitate ease of data management
a standard set of folders for each area of interest. The following creates the needed folders for
the area of interest: _CanyonCreek_. In addition, `fstr` stores a named list of the folders created
which we will utilize later (e.g. to programmatically place results of functions in the correct place).

_Note: if the folders have been generated previously this function will still return the list of
folder names.



Load the spatial data
```{r}
# Read in the aoi data from the test data 
aoi_raw <- system.file("extdata", "aoi.gpkg", package ="PEMprepr")
aoi_raw <- st_read(aoi_raw)

# or read in local aoi 
#aoi_raw <- st_read(file.path("CanyonCreek", "00_raw_inputs", "vector", "aoi.gpkg"))

sf::st_bbox(aoi_raw) ## note extent

```

One concern, with this _area-of-interest_ (`aoi`) is that the bounding box
or geographic extent of the area ends with very random numbers (output above).  Using this extent will cause significant problems later when we attempt to stack numerous rasters.


## Snap the extent

Here the `aoi` is snapped to an extent divisible by 100.  This will facilitate the generation of rasters data that all fits this grid extent and thereby can be stacked with relative ease.

```{r}
# snap the aoi to a standard extent (expand or shrink)
aoi <- aoi_snap(aoi_raw, "expand")
aoi_shrink <- aoi_snap(aoi_raw, "shrink")

mapview::mapview(aoi)
mapview::mapview(aoi_shrink)

sf::st_bbox(aoi)
sf::st_bbox(aoi_shrink)

# write out (this will be added to function later on)
sf::st_write(aoi, file.path(fid$shape_dir_1010[1], "aoi_snapped.gpkg"))

```


# Collection of vector data

A standard set of Vector data is used for subsequent sample planning and is based on the `aoi`.  This script collects numerous vector layers from the [BC Data Catalogue](https://catalogue.data.gov.bc.ca) making use of the [`bcdata`](https://github.com/bcgov/bcdata) package. Files are saved in _geopackage_ format.

```{r, eval=FALSE}
aoi <- st_read(file.path(fid$shape_dir_1010[1], "aoi_snapped.gpkg"))
#aoi <- st_read("D:/PEM_DATA/BEC_DevExchange_Work/DateCreek_AOI/0_raw_inputs/base_layers/aoi.gpkg")

create_base_vectors(in_aoi = aoi,
                    out_path = fid$shape_dir_0010[1])

v <- list.files(path = fid$shape_dir_0010[1], pattern = ".gpkg",
                recursive = TRUE)

v

```

files are saved in _geopackage_ format.

Once the vector data is reviewed and edited where appropriate we can save a final version in the "clean input data folder". 

```{r}

origindir <- fid$shape_dir_0010[1]
filestocopy <- list.files(path = fid$shape_dir_0010[1], pattern = ".gpkg",recursive = TRUE)

targetdir <- fid$shape_dir_1010[1]

lapply(filestocopy, function(x) file.copy(paste (origindir, x , sep = "/"),  
          paste (targetdir,x, sep = "/"), recursive = FALSE,  copy.mode = TRUE))

#file.remove(filestocopy)

```


## Prepare raster outputs 

## Raster templates

The snapped `aoi` can be used to create a raster template.  In the example below a 25m^2^ raster template is created.

```{r}

# create a blank raster template
r5 <- create_template(aoi, 5)
#r10 <- create_template(aoi, 10)
r25 <- create_template(aoi, 25)

```

# Generation of raster covariates

Here we generate the terrain derived covariates.  This is powered by [SAGA-GIS](https://saga-gis.sourceforge.io/en/index.html).  Covariates are generated at multiple resolutions, for example 5, 10, and 25m^2^.

Steps to create the covariates

1. load a digital terrain model (`dtm`).  Generally, this will be a high resolution model derived from lidar.
2. align the `dtm` to the template.  resample the `dtm` to the desired resolution -- here we demonstrate using the 25m^2^ templated created above.
3. create the covariates

## Import the terrain model

```{r}

# read in base DEM and align the dEM
dem <- system.file("extdata", "DTM.tif",package = "PEMprepr")
dem <- terra::rast(dem)

## or alternate  get external TRIM data for DEM

library(bcmaps)
#trim_raw <- cded_raster(aoi_landscape)
trim_raw <- cded_raster(aoi)

# convert the trim to matching raster 
trim <- terra::rast(trim_raw)
trim <- terra::project(trim, r25)

# 5m resolution option 
trim <- terra::rast(trim_raw)
trim5 <- terra::project(trim, r5)

# need to save and then input filepath rather than the actual Dem



```

## Create the covariates

Note that the pre-defined output directory `fid$cov_dir_1020[2]`, created using `setup_folders()`, is used to ensure generated covariates are saved to the correct location. Rasters are also saved into subfolders of the same resolution.


```{r, eval=FALSE}

layer_options <- c("sinksfilled", "sinkroute", "dem_preproc", "slope_aspect_curve",
               "tcatchment", "tca", "scatchment", "twi", "channelsnetwork",
               "overlandflow", "overlandflow2", "multiresflatness", "multiresflatness2",
               "multiresflatness3", "tri", "convergence", "openness",
               "dah", "tpi", "ridgevalley", "mrn", "flowaccumulation",
               "slopelength", "flowaccumulation2", "flowaccumulation3",
               "flowpathlength", "flowpathlength2", "flowpathlength3", "lsfactor",
               "solarrad", "convexity", "vertdistance", "tci_low",
               "swi", "windexp", "texture", "protection", "vrm",
               "mbi", "mscale_tpi", "relposition", "slopecurvatures",
               "steepestslope", "upslopearea")

# run a test covariate
create_covariates(dtm = trim5,           ## raster created above
                  SAGApath = "C:/SAGA/saga-7.7.0_x64/", ## Where SAGA GIS is installed
                  output = fid$cov_dir_1020[2], ## from the setup_folders above
                  layers = "sinksfilled")        ## test one is working 

# run all covariates 
create_covariates(dtm = trim5,           ## raster created above
                  SAGApath = "C:/SAGA/saga-7.7.0_x64/", ## Where SAGA GIS is installed
                  output = fid$cov_dir_1020[2], ## from the setup_folders above
                  layers = c( "all"))       ## use all or one of the above

```


check the list of covariates. Notes these are saved in sdat format.

<center>
_Note: As SAGA-GIS is used the files resulting files are all saved in `.sdat` format -- this is read/writable by `terra::rast`_
</center>


```{r, eval=FALSE}

l <- list.files(path = fid$cov_dir_1020[2], pattern = ".sdat$",
                recursive = TRUE)

l 
```


Create a bec raster to match the template sizes 

```{r}

bec_sf <- sf::st_read(file.path(fid$shape_dir_1010[1], "bec.gpkg")) %>%
  sf::st_cast(., "MULTIPOLYGON") 

bec_code <- bec_sf %>% st_drop_geometry()  %>% dplyr::select(MAP_LABEL) %>%
    unique() 

bec_code <- bec_code %>% 
    mutate(bgc_unique_code = seq(1, length(bec_code$MAP_LABEL),1))

bec_sf <- dplyr::left_join(bec_sf, bec_code)


bec_vec <- terra::vect(bec_sf)

# generate a 25m raster

bec_ras25 <- terra::rasterize(bec_vec, r25, field = "MAP_LABEL")

terra::writeRaster(bec_ras25, file.path(fid$cov_dir_1020[2], "25m", "bec.tif"), overwrite = TRUE)


# generate a 5m raster 

bec_ras5 <- terra::rasterize(bec_vec, r5, field = "MAP_LABEL")

terra::writeRaster(bec_ras5, file.path(fid$cov_dir_1020[2], "5m", "bec.tif"), overwrite = TRUE)

```



# Create the suplementary data. 
## Create fuzzy matrix 

```{r}

#create_fuzzy_matrix()

```

